Silica-based integrated 1$\times$4 polarization beam splitter module for free-space BB84 quantum key distribution

### 2017-09-04 manuscript.tex
some typos were corrected

The need for alignment of discrete optic components can be removed if they are replaced by  a passive photonic chip with integrated elements
%If the optical components are replaced by integrated elements on a chip
fabricated through semiconductor processes such as photo-lithography and dry etching.
The chip-scale integration of the optical part of BB84 system provides miniaturization necessary to diversify application area such as QKD for hand-held devices, and makes it possible to achieve mass production with low cost.
In view of performace, the integration improves stability of QKD system because optical transmission characteristics of a passive photonic chip is quite stable.
%Integration of all the components on a chip removes the alignment processes and prevents the drift of alignment over time that can degrade system stability even though initial alignment status results in sufficiently low QBER.
%The chip-scale integration provides performance stability improvement as well as miniaturization of optical part in BB84 system, and can readily be implemented using waveguide-based photonic circuit technology.
PBS chips using waveguide are widely used in optical receivers for polarization-multiplexed modulation formats such as dual polarization quadrature phase shift keying (DP-QPSK), dual polarization 16 quadrature amplitude modulation (DP-16QAM), etc  \cite{Lee:2016bg,PoDong:2014kj}.
However, there has been no report on integrated PBS chip that can deal with four polarizations used in BB84 QKD.
In this study, integrated PBS module using  silica-based planar lightwave circuit (PLC) chip was fabricated for the first time for BB84 protocol, and its performance was assessed it in a free-space QKD test-bed.

@@

The phase relationship is determined by arm length, as described above.
But actually it changes sensitively with ambient temperature around the interferometer structure.
%따라서 본 연구에서는 간섭계의 arm에 히터를 장착하여 전류로 위상을 조절할 수 있도록 했다.
Therefore, micro-heaters were deposited on the arms of MZI to actively control the phase making use of the themo-optic property of silica.

>>>>

The need for alignment of discrete optic components can be removed if they are replaced by  a passive photonic chip with integrated elements
%If the optical components are replaced by integrated elements on a chip
fabricated through semiconductor processes such as photo-lithography and dry etching.
The chip-scale integration of the optical part of BB84 system provides miniaturization necessary to diversify application area such as QKD for hand-held devices, and makes it possible to achieve mass production with low cost.
In view of performance, the integration improves stability of QKD system because optical transmission characteristics of a passive photonic chip is quite stable.
%Integration of all the components on a chip removes the alignment processes and prevents the drift of alignment over time that can degrade system stability even though initial alignment status results in sufficiently low QBER.
%The chip-scale integration provides performance stability improvement as well as miniaturization of optical part in BB84 system, and can readily be implemented using waveguide-based photonic circuit technology.
PBS chips using waveguide are widely used in optical receivers for polarization-multiplexed modulation formats such as dual polarization quadrature phase shift keying (DP-QPSK), dual polarization 16 quadrature amplitude modulation (DP-16QAM), etc  \cite{Lee:2016bg,PoDong:2014kj}.
However, there has been no report on integrated PBS chip that can deal with four polarizations used in BB84 QKD.
In this study, integrated PBS module using  silica-based planar lightwave circuit (PLC) chip was fabricated for the first time for BB84 protocol, and its performance was assessed it in a free-space QKD test-bed.

@@

The phase relationship is determined by arm length, as described above.
But actually it changes sensitively with ambient temperature around the interferometer structure.
%따라서 본 연구에서는 간섭계의 arm에 히터를 장착하여 전류로 위상을 조절할 수 있도록 했다.
Therefore, micro-heaters were deposited on the arms of MZI to actively control the phase making use of the thermo-optic property of silica.
